Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-07-05 WSSSPE2_report/WSSSPE2_review.tex
Clarify LBNL.

The group came up with the following actions to be performed:
\begin{enumerate}
\item Build a tool that can automatically determine who the contributors are
(from a Git or other repository), then allows the user to manually edit the output to
add/remove people, define roles.
\item Work with repositories to encourage them to provide the information we
need based on what they already store.
\item Define what a citation file should look like and what it should be called.
\item Test adoption, for example, with LBNL. \choinote{what is LBNL?}
\item Create credit file for a set of software.
\item Build a validator (and perhaps a visualizer) for credit files.
\item Write a tool to collect files and visualize/output interconnections (which
software is used with which), based on an existing project.
\item When we (the group members) write papers, we should track the software
we use, and encourage the software developers to make their software citable
and create credit files.
\item Build a tool to export the credit file to BibTex and other citation styles.
\item Make sure the BibTex entries (exported from internal data) are somewhat
standardized so that they can be imported into papers.  Also make sure that
standard LaTeX style files understand and accept these entries.
\end{enumerate}

@@

At the start of the discussion, the breakout group brought forth the important
observation of the wide disparity in commonly accepted habits of publication in
different research fields. In domains which have, historically, relied on large
groups of researchers collaborating towards a common goal (e.g., high-energy
physics, astronomy), publications often have tens or even hundreds of co-authors
(with some papers in experimental particle physics having over 3000.) In other
domains, the number of co-authors is typically much smaller, with, in some
cases, even a preference for single-author papers. Similarly, the various
platforms for publication are valued differently in different domains. Most
commonly, publications in peer-reviewed scientific journals are regarded as the
most important and most impactful. However, in certain domains, especially in
Computer Science, many researchers typically regard conference proceedings as
their prime publication target. It is often suggested that this difference is
due to the rapid developments in information technology, a pace that can not be
upheld by traditional peer-reviewed journals. Whatever the causes, any useful
taxonomy of contributorship or guideline for tenure review should take such
differences into account.

>>>>

The group came up with the following actions to be performed:
\begin{enumerate}
\item Build a tool that can automatically determine who the contributors are
(from a Git or other repository), then allows the user to manually edit the output to
add/remove people, define roles.
\item Work with repositories to encourage them to provide the information we
need based on what they already store.
\item Define what a citation file should look like and what it should be called.
\item Test adoption with a substantial scientific organization such as LBNL (Lawrence Berkeley National Laboratory).
\item Create credit file for a set of software.
\item Build a validator (and perhaps a visualizer) for credit files.
\item Write a tool to collect files and visualize/output interconnections (which
software is used with which), based on an existing project.
\item When we (the group members) write papers, we should track the software
we use, and encourage the software developers to make their software citable
and create credit files.
\item Build a tool to export the credit file to BibTex and other citation styles.
\item Make sure the BibTex entries (exported from internal data) are somewhat
standardized so that they can be imported into papers.  Also make sure that
standard LaTeX style files understand and accept these entries.
\end{enumerate}

@@

At the start of the discussion, the breakout group brought forth the important
observation of the wide disparity in commonly accepted habits of publication in
different research fields. In domains which have, historically, relied on large
groups of researchers collaborating towards a common goal (e.g., high-energy
physics, astronomy), publications often have tens or even hundreds of co-authors
(with some papers in experimental particle physics having over 3000). In other
domains, the number of co-authors is typically much smaller with, in some
cases, even a preference for single-author papers. Similarly, the various
platforms for publication are valued differently in different domains. Most
commonly, publications in peer-reviewed scientific journals are regarded as the
most important and most impactful. However, in certain domains, especially in
Computer Science, many researchers typically regard conference proceedings as
their prime publication target. It is often suggested that this difference is
due to the rapid developments in information technology, a pace that cannot be
upheld by traditional peer-reviewed journals. Whatever the causes, any useful
taxonomy of contributorship or guideline for tenure review should take such
differences into account.
